---
title: "Sample Analysis"
author: "jschoenbachler & eoutland"
date: "2020-12-22"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

## Introduction

All data files are located within the `data` folder. The data consist of song titles,
artist names, audio features (e.g., key, 'instrumentalness', 'danceability'), 
and lyrics taken from Spotify's 'Christmas Hits' playlist.

Descriptions of audio features can be found [here](https://developer.spotify.com/documentation/web-api/reference/tracks/get-several-audio-features/).
The `key` column has already been translated from integer to seven-letter pitch notation.

## Load data

Load data example here.

```{r load libraries}
library(data.table)
library(ggplot2)
```


```{r load all data}
songDT = fread('data/song_data.csv.gz')
head(songDT, 5)
```

## Use word count function

Pass in the data.table to the function and it will return back a data table with each song name, id, word, and count. You can also pass a list of words to exclude `wordExclude` that will exclude those words from the list.

```{r use word count}
source('code/get_lyric_word_count.R')
lyricDT = getLyricWordCount(songDT)
head(lyricDT, 15)
head(getLyricWordCount(songDT, c('merry', 'holidays')), 15)
```

## Sample analyses of danceable words

We can merge the tables and then figure out which words are the most "danceable" based on a column that comes from spotify.

```{r analyze dance words}
songDT = merge(songDT, lyricDT, by = c('track_id', 'track_name'))
songDT = songDT[, word_danceability := ((count / word_total) * danceability)]
setorder(songDT, -word_danceability)
cols = c('track_name', 'danceability', 'word_total', 'word', 'count', 'word_danceability')
head(songDT[, ..cols], 20)
```

## Sample analysis of song key frequencies

The plot below shows the frequencies of the keys represented in pop songs from Spotify's 'Christmas Hits' playlist.

```{r}

songDT = fread('data/song_data.csv.gz')

theme_set(theme_bw())

#labeller to convert binary mode to major/minor
modeLabels = c('Minor', 'Major')
names(modeLabels) = c(0, 1)

ggplot(data = songDT[genre %like% 'pop']) +
  geom_bar(aes(x = as.factor(key))) +
  facet_grid(~mode, labeller =  as_labeller(modeLabels)) +
  
  ggtitle('Frequencies of pop song keys') +
  xlab('Key')
  
```


```{r}
songDT = fread('data/song_data.csv.gz')
songDT = songDT[,-c("lyrics")]
head(songDT)

l = lm(popularity~artist_2, data=songDT)
summary(l)$coef
ggplot(songDT) + geom_boxplot(aes(x=key, y=popularity, color=key))

```

```{r}
songDT[,artist_num:=1]
songDT[artist_2 != "", artist_num:=artist_num+1]
songDT[artist_3 != "", artist_num:=artist_num+1]
songDT[artist_4 != "", artist_num:=artist_num+1]
songDT[, artist234:=ifelse(artist_num>1,"multiple artists", "single artist")]

ggplot(songDT) + geom_boxplot(aes(x=as.factor(artist_num), y=popularity))
ggplot(songDT) + geom_boxplot(aes(x=artist234, y=popularity, color=artist234))
```


```{r}
songDT[,.N,by=artist_1][N>1]
songDT[artist_1=="Michael Bublé"]
nrow(songDT)
```


```{r}
songDT = fread('data/song_data.csv.gz')
lyricDT = getLyricWordCount(songDT, c("a", "the", "i", "to", "and", "at", "my", "its", "in"))
lyricDT[, ratio:=count/word_total]
songDT = songDT[,-c("lyrics")]
songDT2 = merge(songDT, lyricDT, by = c('track_id', 'track_name'))

songDT2[genre %like% "country"][order(popularity, ratio, decreasing = T)][,.(track_name, artist_1, word)][1:10]
songDT2[genre %like% "jazz"][order(popularity, ratio, decreasing = T)][,.(track_name, artist_1, word)][1:10]
songDT2[genre %like% "rock"][order(popularity, ratio, decreasing = T)][,.(track_name, artist_1, word)][1:10]

# songDT[genre %like% "country" & !(genre %like% "jazz") & !(genre %like% "rock"), genre2:="country"]
# songDT[genre %like% "jazz" & !(genre %like% "country") , genre2:="jazz"]
# songDT[genre %like% "rock" & !(genre %like% "country"), genre2:="jazz"]

```

