---
title: "Sample Analysis"
author: "jschoenbachler & eoutland"
date: "2020-12-22"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

## Introduction

All data files are located within the `data` folder. The data consist of song titles,
artist names, audio features (e.g., key, 'instrumentalness', 'danceability'), 
and lyrics taken from Spotify's 'Christmas Hits' playlist.

Descriptions of audio features can be found [here](https://developer.spotify.com/documentation/web-api/reference/tracks/get-several-audio-features/).
The `key` column has already been translated from integer to seven-letter pitch notation.

## Load data

Load data example here.

```{r load libraries}
library(data.table)
library(ggplot2)
library(ggbeeswarm)
library(stringr)
library(viridis)
```


```{r load all data}
songDT = fread('data/song_data.csv.gz')
head(songDT, 5)
```

```{r energy by ! and oh}
songDT[, '"!"' := str_count(lyrics, '!')]
songDT[, '"Oh"' := str_count(lyrics, 'oh')]
songDT[, '"God"' := str_count(lyrics, 'God')]
songMelt = melt(songDT, measure.vars = c('"!"', '"Oh"', '"God"'))
energyByWord = ggplot(data = songMelt, mapping = aes(
  x = value,
  y = energy,
  color = tempo
)) + 
  geom_quasirandom() +
  facet_wrap(~variable, nrow = 3) +
  theme_classic() +
  labs(
    x = 'Word Frequency',
    y = 'Energy Level\n(Meaningful Units)',
    color = 'Tempo',
    title = 'Song Energy by Particular Word Frequency'
  ) +
  scale_color_viridis()
energyByWord
```
<!-- ## Use word count function -->

<!-- Pass in the data.table to the function and it will return back a data table with each song name, id, word, and count. You can also pass a list of words to exclude `wordExclude` that will exclude those words from the list. -->

<!-- ```{r use word count} -->
<!-- source('code/get_lyric_word_count.R') -->
<!-- lyricDT = getLyricWordCount(songDT) -->
<!-- head(lyricDT, 15) -->
<!-- head(getLyricWordCount(songDT, c('merry', 'holidays')), 15) -->
<!-- ``` -->

<!-- ## Sample analyses of danceable words -->

<!-- We can merge the tables and then figure out which words are the most "danceable" based on a column that comes from spotify. -->

<!-- ```{r analyze dance words} -->
<!-- songDT = merge(songDT, lyricDT, by = c('track_id', 'track_name')) -->
<!-- songDT = songDT[, word_danceability := ((count / word_total) * danceability)] -->
<!-- setorder(songDT, -word_danceability) -->
<!-- cols = c('track_name', 'danceability', 'word_total', 'word', 'count', 'word_danceability') -->
<!-- head(songDT[, ..cols], 20) -->
<!-- ``` -->

<!-- ## Sample analysis of song key frequencies -->

<!-- The plot below shows the frequencies of the keys represented in pop songs from Spotify's 'Christmas Hits' playlist. -->

<!-- ```{r} -->

<!-- songDT = fread('data/song_data.csv.gz') -->

<!-- theme_set(theme_bw()) -->

<!-- #labeller to convert binary mode to major/minor -->
<!-- modeLabels = c('Minor', 'Major') -->
<!-- names(modeLabels) = c(0, 1) -->

<!-- ggplot(data = songDT[genre %like% 'pop']) + -->
<!--   geom_bar(aes(x = as.factor(key))) + -->
<!--   facet_grid(~mode, labeller =  as_labeller(modeLabels)) + -->

<!--   ggtitle('Frequencies of pop song keys') + -->
<!--   xlab('Key') -->

<!-- ``` -->
